Refinements for open automata

### 2022-06-02 2021-Refinement/paper/refinementarticle.tex
small changes
proof thm to discuss

We define here simulation between labelled transition systems to Hole-equal simulation  between  open automata that have exactly the same holes.
\begin{definition}[Hole-equal simulation]
Consider two OAs \(\OAg[1]\) and \(\OAg[2]\) with  \(J_1 = J_2\), the relation on configurations \(R: S_1 \times S_2 \to \rformulas[V_1 \uplus V_2]\) is a hole-\(\symb{equal}\) simulation from $S_1$ to $S_2$ if the following conditions hold: 
\item[(1)] \(\sigma_{01} \uplus \sigma_{02} \vdash R\mpar{s_{01}, s_{02}}\)
\item[(2)] \(\forall \mpar{s_1, s_2} \in S_1 \times S_2,\)\vspace{-8pt}
\noindent\begin{multline*}
\everymath{\displaystyle}\begin{array}{l}
		\bigsymb{\forall} t_1 = \OTx{1}{}{1}{1} \in \fOT{s_1}, \bigsymb{\exists} \mpar{t_{2x} = \OTx{2}{x}{2x}{2x} \in \fOT{s_2}}^{x \in X}, \\[10pt]
		\quad \mpar{\forall x \in X, J'_{2x}= J'_1} \\[2pt]
		\nwedge V_1 \uplus V_2 \uplus \fvars{t_1} \vdash\\
\hspace{5em} \left( R\mpar{s_1, s_2} \wedge g_1 \implies \operatorname*{\bigsymb{\bigvee}}_{x \in X} \mpar{\begin{array}{l}
			\alpha_1 = \alpha_{2x} \wedge \bigwedge_\subbox{j \in J'_{2x}} \beta_{1j} = \beta_{2xj} \\[12pt]
			\nwedge g_{2x} \wedge R\mpar{s'_1, s'_{2x}}\psubst{\psi_1 \uplus \psi_{2x}}
		\end{array}}\right)
	\end{array} 
%\\
%	\wedge \mpar{V_1 \uplus V_2 \uplus \biguplus_\subbox{t_2 \in \fOT{s_2}} \fvars{t_2} \vdash R\mpar{s_1, s_2} \wedge \bigvee_\subbox{t_2 \in \fOT{s_2}} \fguard{t_2} \implies \bigvee_\subbox{t_1 \in \fOT{s_1}} \fguard{t_1}}
\end{multline*}
\item[(3)] $R$ is  is preserved along simultaneous transitions of \(A_1\) and \(A_2\).
\end{definition}

@@

In the following definition we add a parameter $H$ which is the set of holes tracked by the refinement relation and adapt the definition by ignoring actions of the holes that are not in $H$.
\begin{definition}[Open automata refinement]\label{Def:OA-Refinement}
For two open automata\\ \(A_1 \defobject \OA{S_1}{s_{01}}{J_1}{V_1}{\sigma_{01}}{T_1}\) and \(A_2 \defobject \OA{S_2}{s_{02}}{J_2}{V_2}{\sigma_{02}}{T_2}\), \(A_1\) is a refinement of \(A_2\) tracking holes \(H\), noted \(\wrel{A_1}{A_2}{H}\), with \(H \subseteq J_1 \cap J_2\), if there is a relation $R: \mpar{S_1 \times S_2} \to \rformulas[V_1 \uplus V_2]$ such that:
\item[(1)] \(\sigma_{01} \uplus \sigma_{02} \vdash R\mpar{s_{01}, s_{02}}\)
\item[(2)] \(\forall \mpar{s_1, s_2} \in S_1 \times S_2,\)
\begin{multline*}
	\everymath{\displaystyle}\begin{array}{l}
		\bigsymb{\forall} \OTx{1}{}{1}{1} \in \fOT{s_1}, \bigsymb{\exists} \mpar{\OTx{2}{x}{2x}{2x} \in \fOT{s_2}}^{x \in X}, \\[12pt]
		\quad \mpar{\forall x \in X, J'_{2x} \cap H = J'_1 \cap H} \\[1pt]
		\nwedge V_1 \uplus V_2 \uplus \fvars{t_1} \vdash\\\hspace{5em} \mpar{R\mpar{s_1, s_2} \wedge g_1 \implies \operatorname*{\bigsymb{\bigvee}}_{x \in X} \mpar{\begin{array}{l}
			\alpha_1 = \alpha_{2x} \wedge \bigwedge_\subbox{j \in J'_{2x} \cap H} \beta_{1j} = \beta_{2xj} \\
			\nwedge g_{2x} \wedge R\mpar{s'_1, s'_{2x}}\psubst{\psi_1 \uplus \psi_{2x}}
		\end{array}}} 
	\end{array} 
\end{multline*}
\item[(3)] $R$ is preserved along simultaneous transitions of \(A_1\) and \(A_2\).

@@

\item  \TODO{Part to check} Finally, we have to prove the following holds:

@@

Yet according to the relation between   $A_2$ and $A_3$ we have for all $\mpar{s_2,s_3} \in S_2 \times S_3$:
\begin{multline*}
\bigsymb{\forall} \mpar{t_2, t_{3}} = \mpar{\OTx{2}{}{2}{2}, \OTx{3}{}{3}{3}} \in \fOT{s_2} \times \fOT{s_3} \\  V_2 \uplus V_3 \uplus \fvars{t_2} \uplus \fvars{t_3} \vdash \hspace{6cm}\\  R_{23}\mpar{s_2, s_3} \wedge 	g_2 \wedge g_{3} \wedge \alpha_2 = \alpha_{3} \wedge \bigwedge_\subbox{j \in J'_2 \cap J'_{3}} \beta_{2j} = \beta_{3j} \implies  R_{23}\mpar{s'_2, s'_{3}}\psubst{\psi_2 \uplus \psi_3}
\end{multline*}

We can make the conjunction of these two formulas.  For each $s_2 \in S_2$, we remark that  $s_2$  allows to relate $s_1$ and $s_3$ if and only if $R_{12}\mpar{s_1, s_2}\land \mpar{R_{23}\mpar{s_2, s_3}} $. Thus, we get  $\forall \mpar{s_1,s_2,s_3} \in S_1\times S_2 \times S_3$ and $\bigsymb{\forall} \mpar{t_1,t_2, t_{3}}\!=\! \mpar{\OTx{1}{}{1}{1},\OTx{2}{}{2}{2},\OTx{3}{}{3}{3}}\! \in\! \fOT{s_1} \times\fOT{s_2} \times \fOT{s_3}$  
\begin{multline*}
V_1\uplus V_2 \uplus V_3 \uplus \fvars{t_1} \uplus \fvars{t_2} \uplus \fvars{t_3} \vdash \left(R_{12}\mpar{s_1, s_2} \wedge   g_1 \wedge g_{2} \wedge \alpha_1 = \alpha_{2} \wedge \bigwedge_\subbox{j \in J'_1 \cap J'_{2}} \beta_{1j} = \beta_{2j}\right) \wedge\\ \mpar{R_{23}\mpar{s_2, s_3} 
\wedge  g_2 \wedge g_{3} \wedge \alpha_2 = \alpha_{3} \wedge \bigwedge_\subbox{j \in J'_2 \cap J'_{3}} \beta_{2j} = \beta_{3j}} \implies R_{12}\mpar{s'_1, s'_{2}}\psubst{\psi_1 \uplus \psi_2} \wedge R_{23}\mpar{s'_2, s'_{3}}\psubst{\psi_2 \uplus \psi_3}
\end{multline*}
Note that if  $R_{12}\mpar{s_1, s_2}$ or $ \mpar{R_{23}\mpar{s_2, s_3}}$ is false the statement trivially holds.

@@

\TODO{XXXXXXXXXXXXXXXXX}
\item The last formula we need to prove is that the relation is preserved along simultaneous transitions, i.e. for all $\mpar{s_{13}, s_{23}} \in S_{13} \times S_{23}$ and
\begin{multline*}
 \bigsymb{\forall} \mpar{t_{13}, t_{23}} = \mpar{\OTx{13}{}{13}{13}, \OTx{23}{}{23}{23}} \in \fOT{s_{13}} \times \fOT{s_{23}} \\  V_{13} \uplus V_{23} \uplus \fvars{t_{13}} \uplus \fvars{t_{23}} \vdash \hspace{6cm}\\  R'\mpar{s_{13}, s_{23}} \wedge 	g_{13} \wedge g_{23} \wedge \alpha_{13} = \alpha_{23} \wedge \bigwedge_\subbox{j \in J'_{13} \cap J'_{23}} \beta_{13j} = \beta_{23j} \implies  R'\mpar{s'_{13}, s'_{23}}\psubst{\psi_{13} \uplus \psi_{23}}\\
\end{multline*}

According to the refinement relation between  $A_1$ and $A_2$ we have, for all $\mpar{s_1,s_{2}} \in S_1 \times S_2$ and
\begin{multline*}
\bigsymb{\forall} \mpar{t_1, t_{2}} = \mpar{\OTx{1}{}{1}{1}, \OTx{2}{}{2}{2}} \in \fOT{s_1} \times \fOT{s_2} \\  V_1 \uplus V_2 \uplus \fvars{t_1} \uplus \fvars{t_2} \vdash \hspace{6cm}\\  R\mpar{s_1, s_2} \wedge 	g_1 \wedge g_{2} \wedge \alpha_1 = \alpha_{2} \wedge \bigwedge_\subbox{j \in J'_1 \cap J'_{2}} \beta_{1j} = \beta_{2j} \implies  R\mpar{s'_1, s'_{2}}\psubst{\psi_1 \uplus \psi_2}
\end{multline*}

The reachability of a state ensures that $\bigsymb{\forall} t_{13} = \OTx{13}{}{13}{13} \in T_{13}$
\[\fvars{t_{13}} \vdash \left(\reach{A_{13}}\mpar{s_{13}} \wedge g_{13} \implies \reach{A_{13}}\mpar{s_{13}'}\psubst{\psi}\right)\]

~~\\
~~\\

The last formula we need to prove is the following: for all $\mpar{s_{13}, s_{23}} \in S_{13} \times S_{23}$
\begin{multline*}
V_{13} \uplus V_{23} \uplus \biguplus_\subbox{t_{23}\in \fOT{s_{23}}} \fvars{t_{23}} \vdash \\ \left(R^{\prime}\mpar{s_{13}, s_{23}} \wedge \bigvee_\subbox{t_{23} \in \fOT{s_{23}}} \fguard{t_{23}} \implies \bigvee_\subbox{t_1 \in \fOT{s_{13}}} \fguard{t_{13}} \right)
\end{multline*}
Let's start  with the hypothesis of the theorem stating that $\wrel{A_1}{A_2}{H}$, thus we have for all  $\mpar{s_1, s_2} \in S_1 \times S_2$ 
\begin{multline*}
V_1 \uplus V_2 \uplus \biguplus_\subbox{t_2 \in \fOT{s_2}} \fvars{t_2} \vdash \left(R\mpar{s_1, s_2} \wedge \bigvee_\subbox{t_2 \in \fOT{s_2}} \fguard{t_2} \implies \bigvee_\subbox{t_1 \in \fOT{s_1}} \fguard{t_1} \right)
\end{multline*}
We extend the valuation to cover the variables of  $t^2_3$ in $t_{23}$ and using their value in $t_3$ and because the following statement holds: $\fvars{t_{13}} \vdash \reach{A_{13}}\mpar{s_{13}}$, we get:
\begin{multline*}
V_1 \uplus V_2 \uplus \biguplus_\subbox{t_{23} \in \fOT{s_{23}}} \fvars{t_{23}} \vdash\\ \left(R\mpar{s_1, s_2} \wedge \bigvee_\subbox{t_{23} \in \fOT{s_{23}}} \fguard{t_{23}}  \wedge \reach{A_{13}}\mpar{s_{13}} \implies \bigvee_\subbox{t_1 \in \fOT{s_1}} \fguard{t_1}   \wedge \reach{A_{13}}\mpar{s_{13}}\right)
\end{multline*}
We have a second hypothesis stating that the result of the composition \(A_1\subst{A_3}{k}\) is non-blocking, by Definition \ref{Def:Non-blockcomp} we have:
\begin{multline*}
V_{13}  \uplus \biguplus_\subbox{t_1 \in \fOT{s_1}} \fvars{t_1} \vdash \left( \reach{A_{13}}\mpar{s_{13}} \wedge \bigvee_\subbox{t_1 \in \fOT{s_1}} \fguard{t_1} \implies \bigvee_\subbox{t_{13} \in \fOT{s_{13}}} \fguard{t_{13}} \right)
\end{multline*}
By transitivity  we obtain:
\begin{multline*}
V_1 \uplus V_2 \uplus \biguplus_\subbox{t_{23} \in \fOT{s_{23}}} \fvars{t_{23}} \vdash\\ \left(R\mpar{s_1, s_2} \wedge \reach{A_{13}}\mpar{s_{13}} \wedge \bigvee_\subbox{t_{23} \in \fOT{s_{23}}} \fguard{t_{23}}   \implies \bigvee_\subbox{t_{13} \in \fOT{s_{13}}} \fguard{t_{13}}\right)
\end{multline*}

>>>>

We define here simulation between labelled transition systems to Hole-equal simulation  between  open automata that have exactly the same holes.
\begin{definition}[Hole-equal simulation]
Consider two OAs \(\OAg[1]\) and \(\OAg[2]\) with  \(J_1 = J_2\), the relation on configurations \(R: S_1 \times S_2 \to \rformulas[V_1 \uplus V_2]\) is a hole-\(\symb{equal}\) simulation from $S_1$ to $S_2$ if the following conditions hold: 
\item[(1)] \(\sigma_{01} \uplus \sigma_{02} \vdash R\mpar{s_{01}, s_{02}}\)
\item[(2)] \(\forall \mpar{s_1, s_2} \in S_1 \times S_2,\)\vspace{-8pt}
\noindent\begin{multline*}
\everymath{\displaystyle}\begin{array}{l}
		\bigsymb{\forall} t_1 = \OTx{1}{}{1}{1} \in \fOT{s_1}, \bigsymb{\exists} \mpar{t_{2x} = \OTx{2}{x}{2x}{2x} \in \fOT{s_2}}^{x \in X}, \\[10pt]
		\quad \mpar{\forall x \in X, J'_{2x}= J'_1} \nwedge\\[2pt]
		 V_1 \uplus V_2 \uplus \fvars{t_1} \vdash\\
\hspace{5em} \left( R\mpar{s_1, s_2} \wedge g_1 \implies \operatorname*{\bigsymb{\bigvee}}_{x \in X} \mpar{\begin{array}{l}
			\alpha_1 = \alpha_{2x} \wedge \bigwedge_\subbox{j \in J'_{2x}} \beta_{1j} = \beta_{2xj} \nwedge\\[12pt]
			 g_{2x} \wedge R\mpar{s'_1, s'_{2x}}\psubst{\psi_1 \uplus \psi_{2x}}
		\end{array}}\right)
	\end{array} 
%\\
%	\wedge \mpar{V_1 \uplus V_2 \uplus \biguplus_\subbox{t_2 \in \fOT{s_2}} \fvars{t_2} \vdash R\mpar{s_1, s_2} \wedge \bigvee_\subbox{t_2 \in \fOT{s_2}} \fguard{t_2} \implies \bigvee_\subbox{t_1 \in \fOT{s_1}} \fguard{t_1}}
\end{multline*}
\item[(3)] $R$ is  is preserved along simultaneous transitions of \(A_1\) and \(A_2\).
\end{definition}

@@

In the following definition we add a parameter $H$ which is the set of holes tracked by the refinement relation and adapt the definition by ignoring actions of the holes that are not in $H$.
\begin{definition}[Open automata refinement]\label{Def:OA-Refinement}
For two open automata\\ \(A_1 \defobject \OA{S_1}{s_{01}}{J_1}{V_1}{\sigma_{01}}{T_1}\) and \(A_2 \defobject \OA{S_2}{s_{02}}{J_2}{V_2}{\sigma_{02}}{T_2}\), \(A_1\) is a refinement of \(A_2\) tracking holes \(H\), noted \(\wrel{A_1}{A_2}{H}\), with \(H \subseteq J_1 \cap J_2\), if there is a relation $R: \mpar{S_1 \times S_2} \to \rformulas[V_1 \uplus V_2]$ such that:
\item[(1)] \(\sigma_{01} \uplus \sigma_{02} \vdash R\mpar{s_{01}, s_{02}}\)
\item[(2)] \(\forall \mpar{s_1, s_2} \in S_1 \times S_2,\)
\begin{multline*}
	\everymath{\displaystyle}\begin{array}{l}
		\bigsymb{\forall} \OTx{1}{}{1}{1} \in \fOT{s_1}, \bigsymb{\exists} \mpar{\OTx{2}{x}{2x}{2x} \in \fOT{s_2}}^{x \in X}, \\[12pt]
		\quad \mpar{\forall x \in X, J'_{2x} \cap H = J'_1 \cap H} \nwedge\\[1pt]
		 V_1 \uplus V_2 \uplus \fvars{t_1} \vdash\\\hspace{5em} \mpar{R\mpar{s_1, s_2} \wedge g_1 \implies \operatorname*{\bigsymb{\bigvee}}_{x \in X} \mpar{\begin{array}{l}
			\alpha_1 = \alpha_{2x} \wedge \bigwedge_\subbox{j \in J'_{2x} \cap H} \beta_{1j} = \beta_{2xj}   \nwedge\\
			 g_{2x} \wedge R\mpar{s'_1, s'_{2x}}\psubst{\psi_1 \uplus \psi_{2x}}
		\end{array}}} 
	\end{array} 
\end{multline*}
\item[(3)] $R$ is preserved along simultaneous transitions of \(A_1\) and \(A_2\).

@@

\item  Finally, we have to prove the following holds:

@@

Yet according to the relation between   $A_2$ and $A_3$ we have  $\forall \mpar{s_2,s_3} \in S_2 \times S_3$ and
\begin{multline*}
\bigsymb{\forall} \mpar{t_2, t_{3}} = \mpar{\OTx{2}{}{2}{2}, \OTx{3}{}{3}{3}} \in \fOT{s_2} \times \fOT{s_3} \\  V_2 \uplus V_3 \uplus \fvars{t_2} \uplus \fvars{t_3} \vdash \hspace{6cm}\\  R_{23}\mpar{s_2, s_3} \wedge 	g_2 \wedge g_{3} \wedge \alpha_2 = \alpha_{3} \wedge \bigwedge_\subbox{j \in J'_2 \cap J'_{3}} \beta_{2j} = \beta_{3j} \implies  R_{23}\mpar{s'_2, s'_{3}}\psubst{\psi_2 \uplus \psi_3}
\end{multline*}

We can make the conjunction of these two formulas.  For each $s_2 \in S_2$, we remark that  $s_2$  allows to relate $s_1$ and $s_3$ if and only if $R_{12}\mpar{s_1, s_2}\land R_{23}\mpar{s_2, s_3} $. Thus, we get  $\forall \mpar{s_1,s_2,s_3} \in S_1\times S_2 \times S_3$ and $\bigsymb{\forall} \mpar{t_1,t_2, t_{3}}\!=\! \mpar{\OTx{1}{}{1}{1},\OTx{2}{}{2}{2},\OTx{3}{}{3}{3}}\! \in\! \fOT{s_1} \times\fOT{s_2} \times \fOT{s_3}$  
\begin{multline*}
V_1\uplus V_2 \uplus V_3 \uplus \fvars{t_1} \uplus \fvars{t_2} \uplus \fvars{t_3} \vdash\\ \left(R_{12}\mpar{s_1, s_2} \wedge   g_1 \wedge g_{2} \wedge \alpha_1 = \alpha_{2} \wedge \bigwedge_\subbox{j \in J'_1 \cap J'_{2}} \beta_{1j} = \beta_{2j}\right) \wedge \hspace{2.5cm}\\ \mpar{R_{23}\mpar{s_2, s_3} 
\wedge  g_2 \wedge g_{3} \wedge \alpha_2 = \alpha_{3} \wedge \bigwedge_\subbox{j \in J'_2 \cap J'_{3}} \beta_{2j} = \beta_{3j}} \implies\\ R_{12}\mpar{s'_1, s'_{2}}\psubst{\psi_1 \uplus \psi_2} \wedge R_{23}\mpar{s'_2, s'_{3}}\psubst{\psi_2 \uplus \psi_3}
\end{multline*}
Note that if  $R_{12}\mpar{s_1, s_2}$ or $ \mpar{R_{23}\mpar{s_2, s_3}}$ is false the statement trivially holds.

@@

\TODO{To discuss the following:} 
\item The last formula we need to prove is that the relation is preserved along simultaneous transitions, i.e. the following is satisfied  $\forall \mpar{s_{13}, s_{23}} \in S_{13} \times S_{23}$ and
\begin{multline*}
 \bigsymb{\forall} \mpar{t_{13}, t_{23}} = \mpar{\OTx{13}{}{13}{13}, \OTx{23}{}{23}{23}} \in \fOT{s_{13}} \times \fOT{s_{23}} \\  V_{13} \uplus V_{23} \uplus \fvars{t_{13}} \uplus \fvars{t_{23}} \vdash \hspace{6cm}\\  R'\mpar{s_{13}, s_{23}} \wedge 	g_{13} \wedge g_{23} \wedge \alpha_{13} = \alpha_{23} \wedge \bigwedge_\subbox{j \in J'_{13} \cap J'_{23}} \beta_{13j} = \beta_{23j} \implies  R'\mpar{s'_{13}, s'_{23}}\psubst{\psi_{13} \uplus \psi_{23}}\\
\end{multline*}

Let's start  with the hypothesis of the theorem stating that $\wrel{A_1}{A_2}{H}$, thus we have   $\forall \mpar{s_1,s_{2}} \in S_1 \times S_2$ and
\begin{multline*}
\bigsymb{\forall} \mpar{t_1, t_{2}} = \mpar{\OTx{1}{}{1}{1}, \OTx{2}{}{2}{2}} \in \fOT{s_1} \times \fOT{s_2} \\  V_1 \uplus V_2 \uplus \fvars{t_1} \uplus \fvars{t_2} \vdash \hspace{6cm}\\  R\mpar{s_1, s_2} \wedge 	g_1 \wedge g_{2} \wedge \alpha_1 = \alpha_{2} \wedge \bigwedge_\subbox{j \in J'_1 \cap J'_{2}} \beta_{1j} = \beta_{2j} \implies  R\mpar{s'_1, s'_{2}}\psubst{\psi_1 \uplus \psi_2}
\end{multline*}

We have a second hypothesis stating that the result of the composition \(A_1\subst{A_3}{k}\) is non-blocking, by Definition \ref{Def:Non-blockcomp} we have:
\begin{multline*}
V_{13}  \uplus \biguplus_\subbox{t_1 \in \fOT{s_1}} \fvars{t_1} \vdash \left( \reach{A_{13}}\mpar{s_{13}} \wedge \bigvee_\subbox{t_1 \in \fOT{s_1}} \fguard{t_1} \implies \bigvee_\subbox{t_{13} \in \fOT{s_{13}}} \fguard{t_{13}} \right)
\end{multline*}

Based on the definition of reachability of a state (Definition \ref{Def:Reach}) we have $\bigsymb{\forall} t_{13} = \OTx{13}{}{13}{13} \in T_{13}$
\[\fvars{t_{13}} \vdash \left(\reach{A_{13}}\mpar{s_{13}} \wedge g_{13} \implies \reach{A_{13}}\mpar{s_{13}'}\psubst{\psi_{13}}\right)\]
\begin{multline*}
\vdash\\ \underbrace{R\mpar{s_1, s_2} \wedge \reach{A_{13}}\mpar{s_{13}} \wedge \bigwedge_\subbox{v_3\in V_3}  v^1_3=v^2_3\wedge s^1_3=s^2_3}_{R^{\prime}(s_{13},s_{23})}  \wedge \dots \implies \ldots 
\end{multline*}
~~\\
~~\\
\TODO{Until here}
The last formula we need to prove is the following: for all $\mpar{s_{13}, s_{23}} \in S_{13} \times S_{23}$
\begin{multline*}
V_{13} \uplus V_{23} \uplus \biguplus_\subbox{t_{23}\in \fOT{s_{23}}} \fvars{t_{23}} \vdash \\ \left(R^{\prime}\mpar{s_{13}, s_{23}} \wedge \bigvee_\subbox{t_{23} \in \fOT{s_{23}}} \fguard{t_{23}} \implies \bigvee_\subbox{t_1 \in \fOT{s_{13}}} \fguard{t_{13}} \right)
\end{multline*}
Let's start  with the hypothesis of the theorem stating that $\wrel{A_1}{A_2}{H}$, thus we have for all  $\mpar{s_1, s_2} \in S_1 \times S_2$ 
\begin{multline*}
V_1 \uplus V_2 \uplus \biguplus_\subbox{t_2 \in \fOT{s_2}} \fvars{t_2} \vdash \left(R\mpar{s_1, s_2} \wedge \bigvee_\subbox{t_2 \in \fOT{s_2}} \fguard{t_2} \implies \bigvee_\subbox{t_1 \in \fOT{s_1}} \fguard{t_1} \right)
\end{multline*}
We extend the valuation to cover the variables of  $t^2_3$ in $t_{23}$ and using their value in $t_3$ and because the following statement holds: $\fvars{t_{13}} \vdash \reach{A_{13}}\mpar{s_{13}}$, we get:
\begin{multline*}
V_1 \uplus V_2 \uplus \biguplus_\subbox{t_{23} \in \fOT{s_{23}}} \fvars{t_{23}} \vdash\\ \left(R\mpar{s_1, s_2} \wedge \bigvee_\subbox{t_{23} \in \fOT{s_{23}}} \fguard{t_{23}}  \wedge \reach{A_{13}}\mpar{s_{13}} \implies \bigvee_\subbox{t_1 \in \fOT{s_1}} \fguard{t_1}   \wedge \reach{A_{13}}\mpar{s_{13}}\right)
\end{multline*}
We have a second hypothesis stating that the result of the composition \(A_1\subst{A_3}{k}\) is non-blocking, by Definition \ref{Def:Non-blockcomp} we have:
\begin{multline*}
V_{13}  \uplus \biguplus_\subbox{t_1 \in \fOT{s_1}} \fvars{t_1} \vdash \left( \reach{A_{13}}\mpar{s_{13}} \wedge \bigvee_\subbox{t_1 \in \fOT{s_1}} \fguard{t_1} \implies \bigvee_\subbox{t_{13} \in \fOT{s_{13}}} \fguard{t_{13}} \right)
\end{multline*}
By transitivity  we obtain:
\begin{multline*}
V_1 \uplus V_2 \uplus \biguplus_\subbox{t_{23} \in \fOT{s_{23}}} \fvars{t_{23}} \vdash\\ \left(R\mpar{s_1, s_2} \wedge \reach{A_{13}}\mpar{s_{13}} \wedge \bigvee_\subbox{t_{23} \in \fOT{s_{23}}} \fguard{t_{23}}   \implies \bigvee_\subbox{t_{13} \in \fOT{s_{13}}} \fguard{t_{13}}\right)
\end{multline*}
